### 2021-09-02 input/related_work.tex
typos of review

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services host by possibly remote third-party \processes; but
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.
% This section reviews these
% approaches.

@@

Dedicated services possibly hosted by remote third-party \processes
are popular, for they propose the simplest mean to deploy such
service. They must maintain
\begin{inparaenum}[(i)]
\item the list of current replicas along with their respective
  location; and
\item the network topology to determine the closest replica for every
  requesting \process.
\end{inparaenum}

@@

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet, ipfs, mdht, squirrel, coin_19}, but still raises
locality issues where \processes
\begin{inparaenum}[(i)]
\item request to a possibly far away location service the content
  location, and then
\item request the actual content from far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
The hash values are the keys to retrieve the associated content
location.  Before downloading any content, a \node asks for its
location using its key. After a series of round-trips between DHT
servers possibly distant from each others, the \node gets a list of
available replicas. Contrarily to \NAME, such services do not ensure
to include the closest replica.

\noindent In addition, they often do not include distance information
along with replica location. Determining where resides the closest
replica for every requesting \process necessarily involves some
knowledge about the \emph{current} topology.  Maintaining a consistent
view of an ever changing topology across a network is inherently
complicated~\cite{topology-discovery, ospf}.
%%  As for the index, this knowledge about the topology can be either
%% centralized~\cite{topology-discovery} or distributed like in
%% routing protocols such as \underline{O}pen \underline{S}hortest
%% \underline{P}ath \underline{F}irst (OSPF)~\cite{ospf}.
As consequence, the requesting \node ends up downloading from multiple
replica hosts, yet only keeping the fastest answer. \Processes either
waste network resources, or face lower response time.

@@

Cutting out the middleman by hosting a location service on each and
every \process improves response time of content retrieval. However,
it still requires every \process to index every live replica as well
as their respective distance in order to rank them.
%% The opposite approach consists in hosting the index directly on the
%% nodes, avoiding any prior request to access a content.
\underline{N}amed \underline{D}ata \underline{N}etworking
(NDN)~\cite{nlsr} broadcasts information about cache updates to all
\nodes in the system. Having the entire knowledge of all the replica
locations along with distance information carried into messages, each
\node easily determine where the closest copy of specific content
resides, without contacting any remote
service. \underline{C}onflict-\underline{f}ree \underline{r}eplicated
\underline{d}atatype (CRDT)~\cite{shapiro2011crdts} for set data
structures could also implement such a location service. \Processes
would eventually have a set of all replicas, assuming eventual
delivery of messages.
\noindent Such solutions imply that every \process receives every
message, which contradicts with the principles of Edge infrastructures
that aim at reducing the volume of data passing through the
network. On the opposite, each \process running \NAME only registers
its closest replica. This allows \NAME to use scoped broadcast as a
communication primitive to lock down the traffic generated by content
indexing based on distances.
% Such solutions inherently imply that every node will
% eventually receive all messages, contrary to \NAME.

>>>>

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services hosted by possibly remote third-party \processes; but
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.
% This section reviews these
% approaches.

@@

Dedicated services possibly hosted by remote third-party \processes
are popular, for they propose the simplest mean to deploy such a
service. They must maintain
\begin{inparaenum}[(i)]
\item the list of current replicas along with their respective
  location; and
\item the network topology to determine the closest replica for every
  requesting \process.
\end{inparaenum}

@@

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet, ipfs, mdht, squirrel, coin_19}, but still raises
locality issues where \processes
\begin{inparaenum}[(i)]
\item request to a possibly far away location service the content
  location, and then
\item request the actual content from far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
The hash values are the keys to retrieve the associated content
location.  Before downloading any content, a \node asks for its
location using its key. After a series of round-trips between DHT
servers possibly distant from each other, the \node gets a list of
available replicas. Contrarily to \NAME, such services do not ensure
to include the closest replica.

\noindent In addition, they often do not include distance information
along with replica location. Determining where resides the closest
replica for every requesting \process necessarily involves some
knowledge about the \emph{current} topology.  Maintaining a consistent
view of an ever changing topology across a network is inherently
complicated~\cite{topology-discovery, ospf}.
%%  As for the index, this knowledge about the topology can be either
%% centralized~\cite{topology-discovery} or distributed like in
%% routing protocols such as \underline{O}pen \underline{S}hortest
%% \underline{P}ath \underline{F}irst (OSPF)~\cite{ospf}.
As a consequence, the requesting \node ends up downloading from multiple
replica hosts, yet only keeping the fastest answer. \Processes either
waste network resources, or face lower response time.

@@

Cutting out the middleman by hosting a location service on each and
every \process improves response time of content retrieval. However,
it still requires every \process to index every live replica as well
as their respective distance in order to rank them.
%% The opposite approach consists in hosting the index directly on the
%% nodes, avoiding any prior request to access a content.
\underline{N}amed \underline{D}ata \underline{N}etworking
(NDN)~\cite{nlsr} broadcasts information about cache updates to all
\nodes in the system. Having the entire knowledge of all the replica
locations along with distance information carried into messages, each
\node easily determine where the closest copy of specific content
resides, without contacting any remote
service. \underline{C}onflict-\underline{f}ree \underline{r}eplicated
\underline{d}atatype (CRDT)~\cite{shapiro2011crdts} for set data
structures could also implement such a location service. \Processes
would eventually have a set of all replicas, assuming eventual
delivery of messages.
\noindent Such solutions imply that every \process receives every
message, which contradicts the principles of Edge infrastructures that
aim at reducing the volume of data passing through the network. On the
opposite, each \process running \NAME only registers its closest
replica. This allows \NAME to use scoped broadcast as a communication
primitive to lock down the traffic generated by content indexing based
on distances.
% Such solutions inherently imply that every node will
% eventually receive all messages, contrary to \NAME.
